Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Removed redundant libraries already part of tidyverse

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(dplyr)
library(knitr)
library(lubridate)
library(ggplot2)
library(ggcorrplot)
library(kableExtra)
library(arrow)
library(zoo)
library(brms)
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(ggcorrplot)
library(kableExtra)
library(arrow)
library(zoo)
library(brms)
```
